Challenges to transboundary fisheries management in North America under climate change

### 2020-06-12 Ecol/Manuscript_Draft.Rmd
outliers gom

```{r GoM_Environ_outliers, eval = F, echo = F}

@@

<!-- GOMA Outliers analysis -->

```{r FigureS23, eval = T, echo = F, fig.cap = "PChanges in maximum catch potential of yellowtail flounder (Limanda ferruginea) within the study area by mid-century relative to present time. Results for the three global circulation models (GFDL, IPSL, MPIS) used in the current study and two climate change scenarios (Top: High emission – RCP 8.5, Bottom: Low Emission – RCP 2.6). Grid-cells marked in yellow represent discrete areas where average MCP is projected to increase by mid-century."}

>>>>

<!-- GOMA Outliers analysis -->
```{r GoM_Environ_outliers, eval = F, echo = F}

@@

```{r FigureS23, eval = T, echo = F, fig.cap = "Changes in maximum catch potential of yellowtail flounder (*Limanda ferruginea*) within the study area by mid-century relative to present time. Results for the three global circulation models (GFDL, IPSL, MPIS) used in the current study and two climate change scenarios (Top: High emission – RCP 8.5, Bottom: Low Emission – RCP 2.6). Grid-cells marked in yellow represent discrete areas where average MCP is projected to increase by mid-century."}

FigS23 <- readPNG(paste(my_path("F"),"S23.png",sep=""))
grid.raster(FigS23)
